Quality Definitions of Qualities

### 2019-10-01 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Updates to quality definitions document
Updates on quality of sustainability definitions

Software is correct if it matches its specification.

@@

@@

To achieve the qualities listed in Section~\ref{SecQualities}, the documentation
should achieve the qualities listed in this section.  All but the final quality
listed (abstraction), are adapted from the IEEE recommended practise for
producing good software requirements~\cite{IEEE1998}.  Abstraction means only
revealing relevant details, which in a requirements document means stating what
is to be achieved, but remaining silent on how it is to be achieved.
Abstraction is an important software development principle for dealing with
complexity~\cite[p.~40]{GhezziEtAl2003}.  \citet{SmithAndKoothoor2016} present
further details on the qualities of documentation for SCS.

@@

There is no direct tool or method for measuring correctness. One way of building
confidence in correctness is by reviewing to ensure that each requirement stated
is one that the stakeholders and experts desire.  By maintaining traceability,
consistency and unambiguity, we can reduce the occurrence of errors and make the
goal of reviewing for correctness easier.

>>>>

Software is correct if it matches its specification.  There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.

@@

One of the original definitions of sustainability (for systems, not software
specific), and still often quoted, is:

\begin{quotation}
\noindent The ability to meet the needs of the present without compromising the ability of
future generations to meet their own needs \cite{Brundtland1987}.
\end{quotation}

This is the definition used by~\cite{IISD2019}.

To make it more useful, this definition is often split into three dimensions:
social, economic and environmental. \wss{cite UN paper [9] in
  \cite{PenzenstadlerAndHenning2013}}  To this list Penzenstadler and Henning
(2013) have added technical sustainability \cite{PenzenstadlerAndHenning2013}.
Where technical sustainability for software is defined as:

\begin{quotation}
\noindent Technical sustainability has the central objective of long-time
usage of systems and their adequate evolution with changing surrounding
conditions and respective requirements \cite{PenzenstadlerAndHenning2013}.
\end{quotation}

The fourth dimension of technical sustainability is also added
by~\cite{WolframEtAl2017}.  Technical sustainability is the focus on the thesis
by~\cite{Hygerth2016}.

\begin{quotation}
  \noindent Sustainable development is a mindset (principles) and an
  accompanying set of practices that enable a team to achieve and maintain an
  optimal development pace indefinitely~\cite{Tate2005}.
\end{quotation}

Parnas discusses as software aging~\cite{Parnas1994a}.

SCS specific definitions:

\begin{quotation}
  \noindent The concept of sustainability is based on three pillars: the
  ecological, the economical and the social. This means that for a software to
  be sustainable, we must take all of its effects -- direct and indirect -- on
  the environment, the economy and the society into account. In addition, the
  entire life cycle of a software has to be considered: from planning and
  conception to programming, distribution, installation, usage and
  disposal~\cite{Heine2017}.
\end{quotation}

\begin{quotation}
  \noindent The capacity of the software to endure. In other words,
  sustainability means that the software will continue to be available in the
  future, on new platforms, meeting new needs~\cite{Katz2016}.
\end{quotation}

Definition from Neil Chue Hong:
\begin{quotation}
\noindent Sustainable software is software which is:
-- Easy to evolve and maintain
-- Fulfils its intent over time
-- Survives uncertainty
-- Supports relevant concerns (Political, Economic, Social, Technical,
Legal, Environmental)~\cite{Katz2016}.
\end{quotation}

Paper critical of a lack of a definition~\cite{VentersEtAl2014}.

Sounds like definition of maintainability.

Find paper that combines nonfunctional qualities into sustainability.

Sustainability depends on the software artifacts AND the software team AND the
development process.

@@

To achieve the qualities listed in Section~\ref{SecQualities}, the documentation
should achieve the qualities listed in this section.  All but the final quality
listed (abstraction), are adapted from the IEEE recommended practise for
producing good software requirements~\cite{IEEE1998}.  Abstraction means only
revealing relevant details, which in a requirements document means stating what
is to be achieved, but remaining silent on how it is to be achieved.
Abstraction is an important software development principle for dealing with
complexity~\cite[p.~40]{GhezziEtAl2003}.  Correctness was in the above list, so
it is not repeated here.  \citet{SmithAndKoothoor2016} present further details
on the qualities of documentation for SCS.

@@
